---
title: "About"
author: "Anders Ellern Bilgrau"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("shiny")
```

## About

This is the [**shiny**](https://shiny.rstudio.com/) web-application accompanying the [**GMCM**](https://cran.r-project.com/package=GMCM) package[1] for [**R**](https://r-project.com). The application is developed and maintained by [Anders Ellern Bilgrau](https://bilgrau.com). You can read more about the underlying methods employed for unsupervised clustering [here](http://doi.org/10.18637/jss.v070.i02) and [here](https://github.com/AEBilgrau/GMCM#GMCM) and the references therein.

### Availability 
The application is available online at 

> https://gmcm.shinyapps.io 

The application can also be available as a local instance on your own machine via the **GMCM** package. To run the application locally, make sure **GMCM** is installed and run

```{r, eval=FALSE}
GMCM::runGMCM()
```

to start a local shiny server. More information on installing **GMCM** and the prerequisites is found at [CRAN](https://cran.r-project.org/web/packages/GMCM/readme/README.html) or [the repository at GitHub](https://github.com/AEBilgrau/GMCM#installation).

This instance is running **GMCM version `r packageVersion("GMCM")`**.


### Citation
If you use the web-application or **GMCM** package itself, please cite the reference below.

```{r citation, results='asis', echo = FALSE}
cat("1. ")
print(citation("GMCM"), style = "text")
```

In **R** you can run `citation("GMCM")` to get a copy-friendly bibtex format.

---


```{r bug, echo = FALSE, results='asis'}
cat(
as.character(
  shiny::withTags(
    div(
      align = "center", 
      "Anders Ellern Bilgrau",
      HTML("&mdash;"),
      a(href = "https://github.com/AEBilgrau/GMCM", padding = "10px",
        shiny::icon("github")),
      a(href = "https://stackoverflow.com/users/1568306/anders-ellern-bilgrau", 
        shiny::icon("stack-overflow")),
      a(href = "https://scholar.google.dk/citations?user=zQNl61YAAAAJ&hl=en", 
        shiny::icon("google")),
      a(href = "https://www.linkedin.com/in/aebilgrau/", 
        shiny::icon("linkedin")),
      HTML("&mdash;"),
      "2019"
    )
  )
))
```

