---
title: "Bug reports"
author: "Anders Ellern Bilgrau"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("htmltools")
```

## Bug reports

If you encounter a bug or issue with the web-application or package itself, please submit an issue at [the GitHub issues page](https://github.com/AEBilgrau/GMCM/issues). 
Requests for features are also warmly welcome here.
If possible try to describe the issue so it can be reproduced.

Alternatively, if you do not have a github account, feel free to email me at anders.ellern.bilgrau (at) gmail.com with your problems or suggestions.


Please refer to **GMCM version `r packageVersion("GMCM")`** when filing a report.

---

```{r bug, echo = FALSE, results='asis'}
cat(
as.character(
  shiny::withTags(
    div(
      align = "center", 
      "Anders Ellern Bilgrau",
      HTML("&mdash;"),
      a(href = "https://github.com/AEBilgrau/GMCM/labels/shiny",
        shiny::icon("bug")),
      HTML("&mdash;"),
      "2019"
    )
  )
))
```
